% ============================================== %
%
% ABSTRACT.tex
%
%% ============================================== %
\begin{abstract}
    This thesis conducts a detailed comparative study of several Machine Learning models, with a focus on their application to Kinect-based data for classifying human movements. The primary aim of this research is to evaluate these models to determine the most effective ones for accurately classifying movements recorded through Kinect sensors.\\

    Our research begins with a introduction to Kinect technology, highlighting its ability to capture detailed movement data. Following this, we take a look into a range of Machine Learning models, such as Support Vector Machines, Random Forest, Linear Regression, and so on. We test each model to evaluate its accuracy, processing efficiency, and robustness in accurately classifying various movements. 
    
    The core of our comparative analysis is a diverse dataset consisting of several movements captured through a Microsoft Kinect. Our research methodology involves several steps: processing the Kinect data, extracting key features that are characteristic of specific movements, and applying the selected models to this improved data. We evaluate the performance of each model using standard metrics like accuracy, precision, recall, and the F1 score, which provide a complete picture of their effectiveness. \\
    
    Over this study, we gain valuable understanding into the specific strengths and limitations of each model in the context of Kinect-based movement classification. Our findings reveal that some models prove enhanced performance in certain situations, which is influenced by factors like the complexity of the captured movements and the characteristics of the dataset. 
    
    This thesis acts as a useful guide for researchers and professionals. It helps them pick the best models for similar work and sets the stage for more research in this area. This study helps improve how accurately and efficiently we can classify movements using advanced Machine Learning methods, leading to more progress in this field.

\end{abstract}

% ! Uncomment this line when printing the thesis.
\let\cleardoublepage\clearpage