% ============================================== %
%
% Acknowledgements
%
%% ============================================== %
\chapter*{Acknowledgements}

    \addcontentsline{toc}{chapter}{Acknowledgements}

    I would like to express my appreciation to \textbf{Prof. Maurizio Mancini}, whose guidance
    and support were pivotal throughout the development of this thesis. The opportunity to work under 
    your supervision has been a significant milestone in my academic journey, and for that, I am grateful.  
   
    \vspace{2mm} 
    
    \noindent I owe a debt of gratitude to my parents, \textbf{Rodica} and \textbf{Dorin}, whose 
    sacrifices have been the starting point of my success. The hard work and unwavering faith they have
    shown, alongside the monumental decision to emigrate from Romania to Italy for the sake of 
    providing me with a brighter future, have been the driving force of my aspirations and endeavors. 
    Their love and support have been my constant source of strength and inspiration.
    
    \vspace{2mm}

    \noindent A heartfelt thanks to my girlfriend, \textbf{Margherita}, for her enduring patience, 
    encouragement, and love. Her belief in my capabilities and her understanding during the demanding 
    times of this degree have been sources of comfort and motivation. Her presence in my life has been
    a beacon of joy and perserverance.

    \vspace{2mm}
  
    \noindent Last but not least, I would like to thank my two casts, \textbf{Mimmi} and
    \textbf{Shelby}. Their companionship during the long nights of study has been a source of relief and comfort. They have been silent and sleepy witnesses to my struggles and accomplishments, their presence is a constant reminder of the importance of the little things in life.

    \vspace{2mm}

    \textit{To all of you, I am eternally thankful. Your contributions to my life and this work have
    not only helped shape this academic effort but also enriched my personal growth.}